### 2019-09-13 README.Rmd
updated readme

Repository for research projects on LIME applied to the Hamby bullet data.

@@

**Current**

@@

**Oral Prelim**

- schedule
    - can be anytime during the semester 
    - just needs to be 6 months before final defense
    - schedule when it gets closer to the time 
    - schedule 3 or 4 weeks in advance
    - send prelim materials to committee 2 weeks in advance
- materials
    - Chapter 0 (complete)
        - lit review
        - research statement: "this is what this thesis will investigate"
    - Chatper 1 (as close to submission as possible)
        - LIME and shortcomings
        - Dr. Dixon likes to give feedback before submission
    - Chapter 2 (draft)
        - Diagnostics for RF
    - Chapter 3 (some idea)
        - Diagnostics for Bayesian Neural Networks
        - Could switch to chapter 2 if more complete
    - Conclusion (not needed)

**Later**

- LIME diagnostics  
    - turn repetitive code into functions
    - try out different weights
    - change distance matrix in seriation to be 5-# of variables shared between two rows
    - try using distance matrix computed on the feature value with seriation
    - add in feature selection methods to LIME input options
    - think of a way to compute consistency across top two features
    - Siggi suggests refitting the RF model to the perturbations and then continuing with LIME with the RF predictions from the new model - this may help to understand if the problems are due to the sampling procedure or LIME itself
    - he also suggested looking into SMOTE for dealing the imbalance in the classes with sampling
    - compare the simple models based on different number of bins using an F-test
    - look into computing a diversity or consistency measure for the sensitivity analysis
    - include a penalty for the number of parameters when choosing bins
    - look at the AUC after binning
    - compute a likelihood ratio prob TRUE / prob FALSE from the LIME ridge regression
    - try visualizing the features from the test data using dimension reduction and
  coloring them by variables suggested to be important by lime
- explainer models
    - read through papers giving an overview of the current explanation methods
    - look into iml (https://www.youtube.com/watch?v=jP6Rg13PEkQ)
    - look more into Molnar and his adviser Bernd
    - look into [MAPLE](https://blog.ml.cmu.edu/2019/07/13/towards-interpretable-tree-ensembles/)
- understanding LIME
    - read through LIME papers again
    - finish journal on understanding lime (look at the RF in the local region lime is considering to see if it agrees with the lime explanations)
    - try fitting LASSO logistic model and leave one out approach (for multicollinarity)
    - assess lime results on logistic regression models
    - think about how the argmin is accomplished by the LIME R package
    - try retriculate to apply python version of lime
    - look into literature on binning methods
    - think about why R^2 would be better for some binning methods
    - read new paper on Anchor
- simulation with RF
    - think about how to implement a simulation with a random forest
    - look back at 601 notes from Kaiser for model assessment
    - look at Hadley's 'removing the blindfold' for ideas
    - read book Dr. Dixon lent me on sensitivity analyses
- possible improvements to LIME
    - determine the best number of bins to use for each variable
    - try out subsampling idea
- random forests confidence intervals
    - look into papers by Giles Hooker and Lucas Mentch
    - Dr. Nettleton paper
- random forest interpretations
    - read https://www.r-bloggers.com/explaining-predictions-random-forest-post-hoc-analysis-randomforestexplainer-package/

## Contents

>>>>

Repository for research projects on LIME

@@

@@

## Oral Prelim

**Schedule**

- can be anytime during the semester 
- just needs to be 6 months before final defense
- schedule when it gets closer to the time 
- schedule 3 or 4 weeks in advance
- send prelim materials to committee 2 weeks in advance

**Materials**

- Chapter 0 (complete)
    - lit review
    - research statement: "this is what this thesis will investigate"
- Chatper 1 (as close to submission as possible)
    - LIME and shortcomings
    - Dr. Dixon likes to give feedback before submission
- Chapter 2 (draft)
    - Diagnostics for RF
- Chapter 3 (some idea)
    - Diagnostics for Bayesian Neural Networks
    - Could switch to chapter 2 if more complete
- Conclusion (not needed)

## Ideas

**LIME diagnostics**

- turn repetitive code into functions
- try out different weights
- change distance matrix in seriation to be 5-# of variables shared between two rows
- try using distance matrix computed on the feature value with seriation
- add in feature selection methods to LIME input options
- think of a way to compute consistency across top two features
- Siggi suggests refitting the RF model to the perturbations and then continuing with LIME with the RF predictions from the new model - this may help to understand if the problems are due to the sampling procedure or LIME itself
- he also suggested looking into SMOTE for dealing the imbalance in the classes with sampling
- compare the simple models based on different number of bins using an F-test
- look into computing a diversity or consistency measure for the sensitivity analysis
- include a penalty for the number of parameters when choosing bins
- look at the AUC after binning
- compute a likelihood ratio prob TRUE / prob FALSE from the LIME ridge regression
- try visualizing the features from the test data using dimension reduction and
coloring them by variables suggested to be important by lime

**Explainer Models**

- read through papers giving an overview of the current explanation methods
- look into iml (https://www.youtube.com/watch?v=jP6Rg13PEkQ)
- look more into Molnar and his adviser Bernd
- look into [MAPLE](https://blog.ml.cmu.edu/2019/07/13/towards-interpretable-tree-ensembles/)

**Understanding LIME**

- edit details in understanding LIME journal
- look at the RF in the local region lime is considering to see if it agrees with the lime explanations
- try fitting LASSO logistic model and leave one out approach (for multicollinarity)
- assess lime results on logistic regression models
- try retriculate to apply python version of lime
- look into literature on binning methods
- think about why R^2 would be better for some binning methods
- read new paper on Anchor

**Possible Improvements to LIME**

- determine the best number of bins to use for each variable
- try out subsampling idea

**Simulation with RF**

- think about how to implement a simulation with a random forest
- look back at 601 notes from Kaiser for model assessment
- look at Hadley's 'removing the blindfold' for ideas
- read book Dr. Dixon lent me on sensitivity analyses

**Random Forests Confidence Intervals**

- look into papers by Giles Hooker and Lucas Mentch
- Dr. Nettleton paper

**Random Forest Interpretations**

- read https://www.r-bloggers.com/explaining-predictions-random-forest-post-hoc-analysis-randomforestexplainer-package/

## Repository Contents
